Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-10-14 writeup/gz_hubble_data.tex
Adding references to Koekemoer et al. (2007,2011).

Space-based observatories, particularly the \hubble{} (\hst), have been
responsible for the bulk of imaging studies of high-redshift galaxies.
Observations of fields with very deep imaging
\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
providing the angular resolution to distinguish internal structure and
characterise the morphology. While these measurements are helped by the fact
that the angular diameter distance is relatively flat beyond $z>1$ in a flat
$\Lambda$CDM cosmology, the relevant angular scales are only of the order
$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
much of the structure for a Milky Way-sized galaxy out to moderately high
redshifts (at least distinguishing a disk from a bulge), but is limited for
more compact structures. Since the size of galaxies evolves as roughly
$r\propto(1+z)^{-1}$ \citep{mao98,law12a}, the compact sizes of high-redshift
galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
However, the public availability of more than $10^5$~galaxies in archival
imaging has generated a sample with the potential
for statistically-robust studies of galaxy demographics and evolution.

@@

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
    $\sim1.8$~deg$^2$ centred at $\alpha=10^\textrm{h}00^\textrm{m},
    \delta=+02^\circ12^\prime$. Its location near the celestial equator was
    designed to enable coverage by ground-based telescopes in both the Northern and
    Southern Hemispheres, in addition to space-based observatories. The ACS data
    for COSMOS consisted of 1~orbit per pointing with an exposure time of
    2028~seconds in \Iband; 590~total pointings were used to cover the entire
    field. The image resolution was dithered to 0.05~\arcsec/pixel. The 50\%
    completeness magnitude for a galaxy with a half-light radius of
    $0.50^{\prime\prime}$ in \Iband{} was 24.7~mag.

>>>>

Space-based observatories, particularly the \hubble{} (\hst), have been
responsible for the bulk of imaging studies of high-redshift galaxies.
Observations of fields with very deep imaging
\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11,koe11} give the photometric
sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
providing the angular resolution to distinguish internal structure and
characterise the morphology. While these measurements are helped by the fact
that the angular diameter distance is relatively flat beyond $z>1$ in a flat
$\Lambda$CDM cosmology, the relevant angular scales are only of the order
$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
much of the structure for a Milky Way-sized galaxy out to moderately high
redshifts (at least distinguishing a disk from a bulge), but is limited for
more compact structures. Since the size of galaxies evolves as roughly
$r\propto(1+z)^{-1}$ \citep{mao98,law12a}, the compact sizes of high-redshift
galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
However, the public availability of more than $10^5$~galaxies in archival
imaging has generated a sample with the potential
for statistically-robust studies of galaxy demographics and evolution.

@@

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07,koe07} covered an area of
    $\sim1.8$~deg$^2$ centred at $\alpha=10^\textrm{h}00^\textrm{m},
    \delta=+02^\circ12^\prime$. Its location near the celestial equator was
    designed to enable coverage by ground-based telescopes in both the Northern and
    Southern Hemispheres, in addition to space-based observatories. The ACS data
    for COSMOS consisted of 1~orbit per pointing with an exposure time of
    2028~seconds in \Iband; 590~total pointings were used to cover the entire
    field. The image resolution was dithered to 0.05~\arcsec/pixel. The 50\%
    completeness magnitude for a galaxy with a half-light radius of
    $0.50^{\prime\prime}$ in \Iband{} was 24.7~mag.
